Graph Generators for Data Science: A Survey

### 2018-06-03 main.tex
Checking the title and abstract

\begin{abstract}
%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
%...
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world
linking properties, 
or gauging the effectiveness of graph algorithms, techniques and 
applications manipulating these data.
We consider graph generation targeting multiple subfields, such as graph databases, graph data mining ,
graph streaming and machine learning communities, alongside community
detection,
social networks and IoT communities. 
Despite the disparate requirements of graph generators throughout these
communities, we analyze them under a common umbrella, reaching out the
functionalities, the practical usage, and the supported operations of graph generators. 
We argue that
this classification is serving the need of providing data scientists,
researchers and practitioners with the right data generator at hand for
their work.

This survey provides a comprehensive overview of the state-of-the-art graph generators 
by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss
open challenges and missing features of graph generators in view of the 
evolution of data science.

\end{abstract}

@@

\begin{acks}
The authors would like to thank Dr. Kamesh Madduri for numerous consultations and suggestions on the covered areas.
\end{acks}

>>>>

\begin{abstract}
%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
%...
The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data. We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities. Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.

This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
\end{abstract}

@@

\begin{acks}
The authors would like to thank Dr. Kamesh Madduri for consultations and suggestions on the covered areas.
\end{acks}
